Biomass and species richness temporal trends drives the assembly and the disassembly of food-web in natural fish assemblages

### 2021-06-14 paper/manuscript.Rmd
Update tables and figures

---
title: "Biomass and species richness temporal trends drives the assembly and the disassembly of food-web in natural fish assemblages"
author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault and Colin Fontaine
date: \today 
output:
  bookdown::pdf_document2:
    fig_caption: true 
    keep_tex: true
    toc: true
fontsize: 12pt
header-includes:
   - \usepackage{natbib}
   - \usepackage{float}
   - \usepackage[table]{xcolor}
   - \usepackage{multirow}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
number_sections: true
---

@@

theme_set(mytheme)
options(knitr.table.format = "latex")
```
```{r}
net_var_bm <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
      "piel_nind")
net_var_rich <- c("log_bm_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
      "piel_nind")
```

@@

@@

```{r}
loadd(p_fig1_2, sp_relation_plot2, predict_plot2)
theme_set(theme_cowplot())
p_bm <- get_plot_fig1_2(predict_plot = predict_plot2, get_list = TRUE,
  bm_x = "log_bm_std", rich_x = "log_rich_std",
  bm_y = c("ct_ff", "w_trph_lvl_avg", "piel_nind", "piel_bm", "log_rich_std")
  )$bm
names(p_bm) <- c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "piel_nind",
  "piel_bm")
#plot_grid(plotlist = p_bm)

sp_bm <- sp_relation_plot2 %>%
  filter(response == "log_bm_std")
p_sp_bm <- sp_bm$gg
names(p_sp_bm) <- sp_bm$y
```

@@

```{r bm, fig.height = 12, fig.cap=fig_bm_cap}
# Make the label on two lines
top <- plot_grid(plotlist = c(ti[[1]], ti[[2]], ti[[3]], ti[[4]], ti[[5]]), ncol = 2)
fig1 <- plot_grid(top, p_bm[[6]], ncol = 1, rel_heights = c(1, .1))
fig1
```

```{r}
p_rich <- get_plot_fig1_2(
  predict_plot = predict_plot2,
  get_list = TRUE,
  rich_x = "log_rich_std",
  rich_y <- c("ct_ff", "w_trph_lvl_avg", "piel_nind", "piel_bm", "log_bm_std")
  )$rich
names(p_rich) <- c(
  "ct_ff", "w_trph_lvl_avg", "piel_nind",
  "piel_bm", "log_bm_std")
#plot_grid(plotlist = p_rich)

sp_rich <- sp_relation_plot2 %>%
  filter(term == "log_rich_std")
p_sp_rich <- sp_rich$pred_plot
names(p_sp_rich) <- sp_rich$y
```

```{r}
fig2_left <- plot_grid(plotlist = p_rich, ncol = 1)
fig2_right <- plot_grid(plotlist = p_sp_rich, ncol = 1)
# plot_grid(plotlist = list(p_bm[[1]], p_sp_bm[[1]], ), ncol = 1)

trich <- list()
for (i in c("log_bm_std", "w_trph_lvl_avg",  "piel_bm", "piel_nind", "ct_ff")) {
  trich[[i]] <- list(p_rich[[i]], p_sp_rich[[i]])
}
```

```{r rich, fig.height = 12, fig.cap=fig_rich_cap}
# Make the label on two lines
top_rich <- plot_grid(
  plotlist = c(trich[[1]], trich[[2]], trich[[3]], trich[[4]], trich[[5]]),
  ncol = 2)
fig2 <- plot_grid(top_rich, p_rich[[6]], ncol = 1, rel_heights = c(1, .1))
fig2
```

@@

```{r}
model_log_bm_f3y_table_medium[["anova_table"]] %>%
  filter(y %in% net_var_bm) %>%
  select(-mod_summary_table) %>%
  format_anova_table() %>%
  kable(.,
    booktabs = TRUE,
    caption =
      paste0(
      "ANOVA results for the links between the temporal trends of
      community biomass and the temporal trends of the network structure."
    ),
  label = "aov-bm"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_rich_f3y_table_medium[["anova_table"]] %>% 
  filter(y %in% net_var_rich) %>%
  select(-mod_summary_table) %>%
  format_anova_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the temporal trends of species
      richness and the temporal trends of the network structure."
    ),
  label = "aov-rich"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_bm_f3y_table_medium$reg_table %>% 
  filter(y %in% net_var_bm) %>%
  format_reg_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of community biomass and the temporal trends
      of the network structure."),
  label = "reg-bm"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_rich_f3y_table_medium$reg_table %>%
  filter(y %in% net_var_rich) %>%
  format_reg_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of species richness and the temporal trends of
      the network structure."
    ),
  label = "reg-rich"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
rsq %>%
  rename(
    Response = y, Explicative = x, 
    `Squared R` = r.squared, `Adjusted squared R` = adj.r.squared
  ) %>% 
  select(Explicative, Response, everything()) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Squared and adjusted squared R for linear models of spatial relationships."),
  label = "rsq"
      ) %>% # 
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

```{r}
loadd(tab_sp_anova)
```

```{r}
tab_sp_anova$log_bm_std %>%
  filter(y %in% net_var_bm) %>%
  mutate(
    y = str_replace_all(y, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(., booktabs = TRUE,
    caption =
      paste0(
      "ANOVA results for the links between the spatial variation of community
      biomass and the one of network structure."),
  label = "aov-bm-sp"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
tab_sp_anova$log_rich_std %>%
  filter(y %in% net_var_rich) %>%
  mutate(
    y = str_replace_all(y, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(., booktabs = TRUE,
    caption =
      paste0(
      "ANOVA results for the links between the spatial variation of species
      richness and the one of network structure."),
  label = "aov-rich-sp"
      ) %>% #
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
table_rsq_sp <- map2(rsq_sp_mod, names(rsq_sp_mod),
  ~mutate(.x, Explicative = .y) %>%
    select(Explicative, Response, Marginal, Conditional)
) %>%
do.call(rbind, .)
rownames(table_rsq_sp) <- NULL

table_rsq_sp %>%
  filter(Explicative %in% c("log_rich_std", "log_bm_std")) %>%
  mutate(
    Explicative = str_replace_all(Explicative, var_replacement()),
    Response = str_replace_all(Response, var_replacement())
  ) %>%
  kable(., booktabs = TRUE,
    caption =
      paste0(
      "Marginal and conditional squared R for spatial models."),
  label = "rsq-sp"
      ) %>% #
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

>>>>

---
title: "Biomass and species richness temporal trends drives the assembly and the disassembly of food-web in natural fish assemblages"
author: Alain Danet, Maud Mouchet, Loubna El Madouri, Elisa Thébault and Colin Fontaine (ordre non fixé)
date: \today 
output:
  bookdown::pdf_document2:
    fig_caption: true 
    keep_tex: true
    toc: true
fontsize: 12pt
header-includes:
   - \usepackage{natbib}
   - \usepackage{float}
   - \usepackage[table]{xcolor}
   - \usepackage{multirow}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
number_sections: true
---

@@

theme_set(mytheme)
options(knitr.table.format = "latex")
```

```{r}
net_var_bm <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
      "piel_nind")
net_var_rich <- c("log_bm_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
      "piel_nind")
```

@@

\newpage

@@

```{r}
loadd(sp_fig1_2_bm_rich_mono_stable_trends,
  pred_bm_rich_mono_stable_trends)

fig1_2 <- get_plot_rich_bm(
  predict_plot = pred_bm_rich_mono_stable_trends,
  get_list = TRUE,
  rm_legend = FALSE,
  bm_x = "log_bm_std",
  bm_y = c(get_com_str_var(), "log_rich_std", "piel_nind", "piel_bm"),
  rich_y = c(get_com_str_var(), "log_bm_std", "piel_nind", "piel_bm"),
  rich_x = "log_rich_std"
  )
p_bm <- fig1_2$bm
names(p_bm) <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg",
  "piel_bm", "piel_nind")
#plot_grid(plotlist = p_bm)

p_sp_bm <- sp_fig1_2_bm_rich_mono_stable_trends$bm
names(p_sp_bm) <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg",
  "piel_bm", "piel_nind")
```

@@

```{r bm, fig.height = 12, fig.cap=fig_bm_cap}
# Make the label on two lines
fig1 <- plot_grid(plotlist = c(ti[[1]], ti[[2]], ti[[3]], ti[[4]], ti[[5]]), ncol = 2)
fig1
```

```{r}
p_rich <- fig1_2$rich
p_sp_rich <- sp_fig1_2_bm_rich_mono_stable_trends$rich
```

```{r}
trich <- list()
for (i in c("log_bm_std", "w_trph_lvl_avg",  "piel_bm", "piel_nind", "ct_ff")) {
  trich[[i]] <- list(p_rich[[i]], p_sp_rich[[i]])
}
```

```{r rich, fig.height = 12, fig.cap=fig_rich_cap}
# Make the label on two lines
fig2 <- plot_grid(
  plotlist = c(trich[[1]], trich[[2]], trich[[3]], trich[[4]], trich[[5]]),
  ncol = 2)
fig2
```

\newpage

@@

```{r}
loadd(pred_bm_rich_mono_stable_trends, anova_table_bm_rich_mono_stable_trends)
anova_table_bm_rich_mono_stable_trends %>%
  mutate(
    response = str_replace_all(response, var_replacement()),
    term = str_replace_all(term, var_replacement())
  ) %>%
  kable(.,
    booktabs = TRUE,
    row.names = FALSE,
    caption =
      paste0(
      "ANOVA results for the links between the temporal trends of
      community biomass and the temporal trends of the network structure."
    ),
  label = "aov-bm-rich"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
loadd(reg_table_bm_rich_mono_stable_trends)
reg_table_bm_rich_mono_stable_trends %>%
  mutate(
    response = str_replace_all(response, var_replacement()),
    term = str_replace_all(term, var_replacement())
    ) %>%
kable(., booktabs = TRUE,
  row.names = FALSE,
  caption =
    paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of community biomass and the temporal trends
      of the network structure."),
      label = "reg-bm-rich"
      ) %>%
  kable_styling(latex_options = c("scale_down", "striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
loadd(rsq_table_bm_rich_mono_stable_trends)
rsq_table_bm_rich_mono_stable_trends %>%
  mutate(
    Response = str_replace_all(Response, var_replacement())
  ) %>%
  kable(., booktabs = TRUE,
    caption =
      paste0(
      "Marginal and conditional squared R for temporal models."),
  label = "rsq-sp"
      ) %>% #
  kable_styling(latex_options = c("striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

```{r}
loadd(
  sp_anova_table_bm_rich_mono_stable_trends,
  sp_rsq_table_bm_rich_mono_stable_trends
)
```

```{r}
sp_anova_table_bm_rich_mono_stable_trends %>%
  mutate(
    response = str_replace_all(response, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(., booktabs = TRUE,
    caption =
      paste0(
      "ANOVA results for the links among the spatial variation of community
      biomass and species richness and the one of network structure."),
  label = "aov-sp"
  ) %>%
  kable_styling(latex_options = c("scale_down", "striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
sp_rsq_table_bm_rich_mono_stable_trends %>%
  mutate(
    Response = str_replace_all(Response, var_replacement())
  ) %>%
  kable(., booktabs = TRUE,
    caption =
      paste0(
      "Marginal and conditional squared R for spatial models."),
  label = "rsq-sp"
      ) %>% #
  kable_styling(latex_options = c("striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```
